The internals of the Game Boy consist of a CPU, a PPU (\char`\"{}\+Picture Processing Unit\char`\"{}), an APU (\char`\"{}\+Audio Processing Unit\char`\"{}) and (eventually) an additional controller (MBC, \char`\"{}\+Memory Bank Controller\char`\"{}) embedded into the game cartridge. The whole machine runs at a clock speed of $\sim$4\+MHz (\char`\"{}dot clock\char`\"{}) but most operations require multiple of 4 clock cycles to runs, effectively making it a 1MHz clock (\char`\"{}machine clock\char`\"{}).

A very good general overview of the hardware can be found in {\itshape The Ultimate Game Boy Talk}, on \href{https://www.youtube.com/watch?v=HyzD8pNlpwI}{\texttt{ You\+Tube}}.

There does not exist one single official resource that explains {\itshape all} the hardware. Throughout the years, the community has put together a series of references. These are the ones I used for developing my emulator\+:

\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{3}{|X[-1]}|}
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Reference   }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Comment   }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Link    }\\\cline{1-3}
\endfirsthead
\hline
\endfoot
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Reference   }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Comment   }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Link    }\\\cline{1-3}
\endhead
\PBS\centering Pandocs   &Probably the most complete reference for the Game Boy hardware as a whole.   &\href{https://gbdev.io/pandocs/}{\texttt{ https\+://gbdev.\+io/pandocs/}}    \\\cline{1-3}
\PBS\centering GBEDG   &Incomplete \char`\"{}guide\char`\"{} for gameboy emulator development. Explained some PPU concepts better than Pandocs did.   &\href{https://hacktix.github.io/GBEDG/}{\texttt{ https\+://hacktix.\+github.\+io/\+GBEDG/}}    \\\cline{1-3}
\PBS\centering wiki   &Useful for general references.   &\href{https://gbdev.gg8.se/wiki/articles/Main_Page}{\texttt{ https\+://gbdev.\+gg8.\+se/wiki/articles/\+Main\+\_\+\+Page}}    \\\cline{1-3}
\PBS\centering \char`\"{}\+Complete\char`\"{} technical reference   &Useful for implementing/referencing CPU instructions.   &\href{https://gekkio.fi/files/gb-docs/gbctr.pdf}{\texttt{ https\+://gekkio.\+fi/files/gb-\/docs/gbctr.\+pdf}}    \\\cline{1-3}
\PBS\centering CPU Manual   &Official manual from Nintendo. Information here is very inaccurate, but still useful at times.   &\href{http://marc.rawer.de/Gameboy/Docs/GBCPUman.pdf}{\texttt{ http\+://marc.\+rawer.\+de/\+Gameboy/\+Docs/\+GBCPUman.\+pdf}}    \\\cline{1-3}
\PBS\centering Z80 Game development   &Resource that describes some aspects of the Z80 CPU (The Game Boy uses a modified version of the Z80).   &\href{https://jgmalcolm.com/z80/}{\texttt{ https\+://jgmalcolm.\+com/z80/}}    \\\cline{1-3}
\PBS\centering e\+Z80 Heaven   &Additional CPU development resource.   &\href{https://ez80.readthedocs.io/en/latest/index.html}{\texttt{ https\+://ez80.\+readthedocs.\+io/en/latest/index.\+html}}   \\\cline{1-3}
\end{longtabu}
